Datasets

### 2018-08-10 scripts/01-datasets/01-real/README.Rmd

1. The datasets are downloaded from their respective sources (such as GEO) using sets of scripts specific for each dataset in [01-download_from_sources.R](01-download_from_sources.R) (these scripts are located in [helpers-download_from_sources](helpers-download_from_sources))
2. These datasets are filtered and normalised in [02-filter_and_normalise.R](02-filter_and_normalise.R)

>>>>

1. The datasets are downloaded from their respective sources (such as GEO) using sets of scripts specific for each dataset in [01-download_from_sources.R](01-download_from_sources.R) (these scripts are located in [helpers-download_from_sources](helpers-download_from_sources))
2. These datasets are filtered and normalised in [02-filter_and_normalise.R](02-filter_and_normalise.R). This is done using the dynbenchmark::process_raw_dataset function.

Following datasets were ultimately generated:

```{r}
# library(tidyverse)
# library(dynbenchmark)
# list_datasets() %>% 
#   filter(source == "real") %>% 
#   select(name)
```
